%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

%% https://www.grad.ubc.ca/current-students/dissertation-thesis-preparation/preliminary-pages
%% 
%% LAY SUMMARY Effective May 2017, all theses and dissertations must
%% include a lay summary.  The lay or public summary explains the key
%% goals and contributions of the research/scholarly work in terms that
%% can be understood by the general public. It must not exceed 150
%% words in length.

\chapter{Lay Summary}

Internet of Things (IoT) is a network of physical objects that are embedded with sensors or actuators. These \textit{smart objects} can interact together or with human beings to deliver different goals. The number of these smart objects is increasing every year and it is estimated that by 2025, there would be more than 30 Billion IoT-specific devices. IoT systems consist of different layers, from the physical devices to the user-faced applications. IoT developers write code to deliver the goals and responsibilities of each layer. 

In this research, we analyze IoT developers' code and development practices, to characterize their challenges and the types of bugs they usually face. We study the root cause of 323 bugs, interview nine, and survey 193 IoT developers to address the goals of this research. Our findings explain the categories of bugs in IoT systems and their root causes. Additionally, we present the challenges IoT developers face during different stages of development, such as testing and debugging.